Quasi-universal acceptance of basic science in the US

### 2024-09-19 appendix_exp1.Rmd
submission public understanding of science

Beside Belief in Conspiracy Theory Inventory (BCTI) by @pennycookOverconfidentlyConspiratorialConspiracy2022 which report in the main study, we also assessed two other consipiracy thinking measures:

1. The conspiracy mentality questionnaire (CMQ) by @bruderMeasuringIndividualDifferences2013:
I think that . . .

-   ... many very important things happen in the world, which the public is never informed about. - politicians usually do not tell us the true motives for their decisions.
-   ... government agencies closely monitor all citizens.
-   ... events which superficially seem to lack a connection are often the result of secret activities.
-   ... there are secret organizations that greatly influence political decisions.

[0% - 100%; 0 = certainly not, 100 = certain]

2.  The Single Item Conspiracy Beliefs Scale (SICBS) by @lantianMeasuringBeliefConspiracy2016 :

-   I think that the official version of the events given by the authorities very often hides the truth. [1-9; 1 = Completely false, 5 = Unsure, 9 = Completely true]

We rely on three items

1. How much do you trust scientists in this country? Do you trust them a lot, some, not much, or not at all? [1 = Not at all, 2 = Not much, 3 = Some, 4 = A lot]

2. In general, would you say that you trust science a lot, some, not much, or not at all? [1 = Not at all, 2 = Not much, 3 = Some, 4 = A lot]

3. How much confidence do you have in scientists to act in the best interests of the public? [1-5; 1 = No confidence at all, 5 = A great deal of confidence]

@@

Fig. \@ref(fig:exp1-conditional-acceptance) illustrates the relationship between knowledge and acceptance. In most cases (`r exp1_descriptives$conditional_acceptance$false$Yes$share`), participants readily accepted the scientific consensus after having given the wrong answer to a question. In very few cases (`r exp1_descriptives$conditional_acceptance$true$No$share`), participants who gave the correct response afterwards rejected the scientific consensus, thereby contradicting their own initial response. We believe this might have been due to inattention.

For RQ3, we find a positive but small correlation between both science knowledge and trust in science (r = `r exp1_descriptives$cor_trust_knowledge$estimate`, p `r exp1_descriptives$cor_trust_knowledge$p.value`), and acceptance of scientific consensus and trust in science (r = `r exp1_descriptives$cor_trust_acceptance$estimate`, p `r exp1_descriptives$cor_trust_acceptance$p.value`). The more people are knowledgeable about science and the more they tend to accept the scientific consensus, the more they tend to trust science. These correlations are relatively weak, which might be partly due to ceiling effects: As illustrated in Fig. \@ref(fig:exp1-plot), (i) most people do trust science, and (ii) that is true even among people with low knowledge or acceptance rates.

@@

In Appendix \@ref(exp1), we show that these associations are robust when using alternative measures of trust and conspiracy thinking. Appendix \@ref(exp1) also includes more descriptive statistics, such as knowledge and acceptance by science questions.

@@

## By-question variation

```{r}
# calculate share
plot_data <- exp1_long %>% 
  group_by(subject) %>% 
  summarize(share_true = sum(knowledge == TRUE, na.rm = TRUE)/n(),
            share_accepted = sum(acceptance == "Yes", na.rm = TRUE)/n()) 
```

### Knowledge

(ref:exp1-questions-knowledge) Distribution of correct answers by question.

```{r exp1-questions-knowledge, fig.cap="(ref:exp1-questions-knowledge)"}
# plot knowledge
ggplot(plot_data, aes(x = reorder(subject, share_true), y = share_true)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, 0.1)) +
  labs(x = "Question", y = "Share of correct responses") +
  coord_flip()
```

### Acceptance

(ref:exp1-questions-acceptance) Distribution of consensus acceptance by question.

```{r exp1-questions-acceptance, fig.cap="(ref:exp1-questions-acceptance)"}
# plot acceptance
ggplot(plot_data, aes(x = reorder(subject, share_accepted), y = share_accepted)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, 0.1)) +
  labs(x = "Question", y = "Share of acceptance") +
  coord_flip()
```

## Trust in science

(ref:exp1-trust-scientists) Distribution of trust in scientists.

```{r exp1-trust-scientists, fig.cap="(ref:exp1-trust-scientists)"}
# calculate share
plot_data <- exp1_wide %>% 
  group_by(wgm_scientists) %>% 
  summarize(n = n()) %>% 
  ungroup() %>% 
  mutate(share = n/sum(n)) %>% 
  rounded_numbers()

# plot knowledge
ggplot(plot_data, aes(x = wgm_scientists, y = share)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, 0.1)) +
  labs(x = "Trust in science", y = "Share of participants") +
  geom_text(aes(label = paste0(round(share * 100, 1), "%")),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3) 
```

## Conspiracy thinking

### Distribution

(ref:exp1-conspiracy-distribution) Distribution of conspiracy thinking.

```{r exp1-conspiracy-distribution, fig.cap="(ref:exp1-conspiracy-distribution)"}
# plot knowledge
ggplot(exp1_wide, aes(x = BCTI_avg)) +
  geom_histogram() +
  labs(x = "Average conspiracy thinking (BCTI)", y = "N")
```

### By-item variation

(ref:exp1-conspiracy-items) Distribution of conspiracy thinking by item.

```{r exp1-conspiracy-items, fig.cap="(ref:exp1-conspiracy-items)"}
BCTI_data <- exp1_long %>% 
  # bring to long format
  pivot_longer(cols = BCTI_apollo:BCTI_evolution, 
               names_to = "BCTI_item", values_to = "score") %>% 
  select(id, c(starts_with("BCTI"), score)) %>% 
  group_by(BCTI_item) %>% 
  summarize(avg_score = mean(score)) %>% 
  ungroup()

ggplot(BCTI_data, aes(x = reorder(BCTI_item, avg_score), y = avg_score)) +
    geom_pointrange(aes(ymin = 1, ymax = avg_score),
                  # Make the lines a little thicker and the dots a little bigger
                  fatten = 2, size = 1) +
  scale_y_continuous(limits = c(1, 9), breaks = seq(1, 9, 1)) +
  labs(x = "Conspiracy item", y = "Average score") +
  coord_cartesian(ylim = c(1, 9)) +
  coord_flip()
```

## Open ended comments
```{r}
# levels(as.factor(exp1_wide$comments))
table <- exp1_wide %>% 
  drop_na(comments) %>% 
  select(id, comments)

kbl(table, booktabs = T, longtable = TRUE,
    caption = "Reasons for consensus rejection") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2, width = "40em") 
```

## Additional plots

(ref:exp1-conditional-acceptance) Acceptance rates of scientific consensus, based on whether the initial response to the knowledge question was false or true.

```{r exp1-conditional-acceptance, fig.cap="(ref:exp1-conditional-acceptance)"}
plot_data <- exp1_long %>% 
  group_by(knowledge, acceptance) %>% 
  count() %>% 
  group_by(knowledge) %>% 
  mutate (share = n/sum(n)) %>% 
  mutate_if(is.numeric, round, digits = 3)

absolute_numbers <- plot_data %>% 
  group_by(knowledge) %>% 
  summarise(n = sum(n))

ggplot(plot_data, aes(x = knowledge, y = share, fill = acceptance)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, 0.1)) +
  geom_text(aes(label = paste0(round(share * 100, 1), "%")),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3) +
  scale_fill_viridis_d(option = "cividis") +
  labs(x = "Knowledge answer", fill = "Acceptance \nof consensus") +
  plot_theme +
  geom_bracket(data = absolute_numbers,
               aes(xmin = as.numeric(factor(knowledge)) - 0.4, 
                   xmax = as.numeric(factor(knowledge)) + 0.4, 
                   y.position = 1.05, label =  paste0("n = ", n)),
               inherit.aes = FALSE,
               step.increase = 0)
```

(ref:exp1-plot-overview) **A** Shows the distribution of science knowledge (left) and acceptance of scientific consensus **B** Shows the relationship between trust in science and science knowledge/acceptance of scientific consensus **C** Shows the relationship between conspiracy thinking and science knowledge/acceptance of scientific consensus

@@

trust_acceptance <- ggplot(plot_data, aes(x = avg_acceptance, y = wgm_sciencegeneral, fill = n)) +
  geom_tile() +  
  geom_jitter(inherit.aes = FALSE, data = exp1_wide, aes(x = avg_acceptance, y = wgm_sciencegeneral),
              width = 0.03, height = 0.08) + 
  scale_fill_viridis_c(option = "plasma") + 
  scale_x_continuous(breaks = seq(0, 1, 0.1)) +
  coord_cartesian(xlim = c(0, 1)) +
  scale_y_continuous(breaks = 1:5) +
  labs(x = "Average consensus Acceptance", 
       y = "Trust in science", 
       fill = "N") +
  theme(legend.position = "top")

@@

>>>>

In addition to the Belief in Conspiracy Theory Inventory (BCTI) by @pennycookOverconfidentlyConspiratorialConspiracy2022 which report in the main study, we also assessed two other consipiracy thinking measures: The conspiracy mentality questionnaire (CMQ) by @bruderMeasuringIndividualDifferences2013 and the Single Item Conspiracy Beliefs Scale (SICBS) by @lantianMeasuringBeliefConspiracy2016 (Table \@ref(tab:overview-conspiracy-measures)).

```{r overview-conspiracy-measures}
# Create the data for the table
conspiracy_measures <- data.frame(
  Measure = c(
    "Belief in Conspiracy Theory Inventory (BCTI)", 
    "Conspiracy Mentality Questionnaire (CMQ)", 
    "", "", "", "", "",
    "Single Item Conspiracy Beliefs Scale (SICBS)"
  ),
  Description = c(
    "By Pennycook et al., 2022, presented in the main article.", 
    "By Bruder et al., 2013. Respondents are asked how much they agree with the following statements:", 
    "- Many important things happen in the world, which the public is never informed about.",
    "- Politicians usually do not tell us the true motives for their decisions.",
    "- Government agencies closely monitor all citizens.",
    "- Events which seem unrelated are often the result of secret activities.",
    "- There are secret organizations that greatly influence political decisions.",
    "By Lantian et al., 2016. The item is: 'I think that the official version of events given by the authorities very often hides the truth.'"
  ),
  Scale = c(
    "1 - 9 (1 = Completely false, 5 = Unsure, 9 = Completely true)", 
    "0% - 100% (0 = certainly not, 100 = certain)",
    "", "", "", "", "",
    "1 - 9 (1 = Completely false, 5 = Unsure, 9 = Completely true)"
  )
)

# # Create the table
kbl(conspiracy_measures, booktabs = T, longtable = T,
    caption = "Conspiracy measures", full_width = T) %>%
  kable_styling(font_size = 8) %>% 
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "20em") %>%
  column_spec(3, width = "10em")

# Use apa_table to format the table
# apa_table(
#   conspiracy_measures,
#   caption = "Overview of Conspiracy Thinking Measures",
#   align = c("m{4cm}", "m{10cm}", "m{4cm}")
# )
```

@@

In most cases (`r exp1_descriptives$conditional_acceptance$false$Yes$share`), participants readily accepted the scientific consensus after having given the wrong answer to a question. In very few cases (`r exp1_descriptives$conditional_acceptance$true$No$share`), participants who gave the correct response afterwards rejected the scientific consensus, thereby contradicting their own initial response. We believe this might have been due to inattention.

For RQ3, we find a positive but small correlation between both science knowledge and trust in science (r = `r exp1_descriptives$cor_trust_knowledge$estimate`, p `r exp1_descriptives$cor_trust_knowledge$p.value`), and acceptance of scientific consensus and trust in science (r = `r exp1_descriptives$cor_trust_acceptance$estimate`, p `r exp1_descriptives$cor_trust_acceptance$p.value`). The more people are knowledgeable about science and the more they tend to accept the scientific consensus, the more they tend to trust science. These correlations are relatively weak, which might be partly due to ceiling effects: As illustrated in Fig. \@ref(fig:exp1-plot-overview), (i) most people do trust science, and (ii) that is true even among people with low knowledge or acceptance rates.

@@

Below, we show that these associations are robust when using alternative measures of trust and conspiracy thinking. We also provide more descriptive statistics, such as knowledge and acceptance by science questions.

@@

(ref:exp1-plot-overview) Summary plot for Study 1. **A** Shows the distribution of science knowledge (left) and acceptance of scientific consensus **B** Shows the relationship between trust in science and science knowledge/acceptance of scientific consensus **C** Shows the relationship between conspiracy thinking and science knowledge/acceptance of scientific consensus

@@

trust_acceptance <- ggplot(plot_data, aes(x = avg_acceptance, y = wgm_sciencegeneral, fill = n)) +
  geom_tile() +  
  geom_jitter(inherit.aes = FALSE, data = exp1_wide, aes(x = avg_acceptance, y = wgm_sciencegeneral),
              width = 0.03, height = 0.08) + 
  scale_fill_viridis_c(option = "plasma") + 
  scale_x_continuous(breaks = seq(0, 1, 0.1)) +
  coord_cartesian(xlim = c(0, 1)) +
  scale_y_continuous(breaks = 1:5) +
  labs(x = "Average consensus Acceptance", 
       y = "Trust in science", 
       fill = "N")

@@

## Open ended comments

```{r}
# levels(as.factor(exp1_wide$comments))
table <- exp1_wide %>% 
  drop_na(comments) %>% 
  select(id, comments)

kbl(table, booktabs = T, longtable = TRUE,
    caption = "Comments of participants on Study 1") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2, width = "40em") 
```

### 2024-09-19 appendix_exp2.Rmd
submission public understanding of science

In experiment 1, we tested whether participants would accept the scientific consensus on basic science facts. In most instances they did, but not always. In experiment 2, we wanted to test whether this reluctance was because of participants not trusting us as a source of consensual science knowledge. To do so, we added an explanation and sources to each consensus statement, instead of only stating the consensus. To better understand reasons for consensus rejection, after having answered all questions, we asked participants an open-ended question to explain why they rejected the consensus, for each question on which they did so. We also excluded the where do trees their materials from, as this question clearly seemed to be an outlier where most participants would get the answer wrong (see Appendix \@ref(exp1)).

@@

Confirming results from experiment 1, we find that the more people are knowledgeable about science and the more they tend to accept the scientific consensus even when they are not that knowledgeable in science, the more they tend to trust science. These correlations are relatively weak, which might be partly due to ceiling effects: As illustrated in Fig. \@ref(fig:exp2-plot), (i) most people do trust science, and (ii) that is true even among people with low knowledge or acceptance rates. In Appendix \@ref(exp2) we show that these results hold for our alternative measures of trust and conspiracy thinking. We also include more descriptive statistics, such as knowledge and acceptance by science questions.

Regarding RQ1, participants answered on average `r exp2_descriptives$means$knowledge_mean` (sd = `r exp2_descriptives$means$knowledge_sd`) of the questions correctly, and accepted the scientific consensus on average for `r exp2_descriptives$means$acceptance_mean` (sd = `r exp2_descriptives$means$acceptance_sd`) of the questions. Fig. \@ref(fig:exp2-conditional-acceptance) illustrates the relationship between knowledge and acceptance. In response to RQ2, in most cases (`r exp2_descriptives$conditional_acceptance$false$Yes$share`), participants readily accepted the scientific consensus after having initially given the wrong answer to a question. In very few cases (`r exp2_descriptives$conditional_acceptance$true$No$share`), participants who gave the correct response afterwards rejected the scientific consensus, thereby contradicting their own initial response.

@@

For RQ3, we got `r exp2_descriptives$justifications_n` answers from `r exp2_descriptives$justifications_n_participants` different participants to the open-ended questions on why they had rejected the scientific consensus on a particular question. Table \@ref(tab:exp2-justifications) summarizes these answers by five categories. All answers can be read in Appendix \@ref(exp2).

@@

## By-question variation

```{r}
# calculate share
plot_data <- exp2_long %>% 
  group_by(subject) %>% 
  summarize(share_true = sum(knowledge == TRUE, na.rm = TRUE)/n(),
            share_accepted = sum(acceptance == "Yes", na.rm = TRUE)/n()) 
```

### Knowledge

(ref:exp2-questions-knowledge) Distribution of correct answers by question.

```{r exp2-questions-knowledge, fig.cap="(ref:exp2-questions-knowledge)"}
# plot knowledge
ggplot(plot_data, aes(x = reorder(subject, share_true), y = share_true)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, 0.1)) +
  labs(x = "Question", y = "Share of correct responses") +
  coord_flip()
```

### Acceptance

(ref:exp2-questions-acceptance) Distribution of consensus acceptance by question.

```{r exp2-questions-acceptance, fig.cap="(ref:exp2-questions-acceptance)"}
# plot acceptance
ggplot(plot_data, aes(x = reorder(subject, share_accepted), y = share_accepted)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, 0.1)) +
  labs(x = "Question", y = "Share of acceptance") +
  coord_flip()
```

## Trust in science

(ref:exp2-trust-scientists) Distribution of trust in scientists.

```{r exp2-trust-scientists, fig.cap="(ref:exp2-trust-scientists)"}
# calculate share
plot_data <- exp2_wide %>% 
  group_by(wgm_scientists) %>% 
  summarize(n = n()) %>% 
  ungroup() %>% 
  mutate(share = n/sum(n)) %>% 
  rounded_numbers()

# plot knowledge
ggplot(plot_data, aes(x = wgm_scientists, y = share)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, 0.1)) +
  labs(x = "Trust in science", y = "Share of participants") +
  geom_text(aes(label = paste0(round(share * 100, 1), "%")),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3) 
```

## Conspiracy thinking

### Distribution

(ref:exp2-conspiracy-distribution) Distribution of conspiracy thinking.

```{r exp2-conspiracy-distribution, fig.cap="(ref:exp2-conspiracy-distribution)"}
# plot knowledge
ggplot(exp2_wide, aes(x = BCTI_avg)) +
  geom_histogram() +
  labs(x = "Average conspiracy thinking (BCTI)", y = "N")
```

### By-item variation

(ref:exp2-conspiracy-items) Distribution of conspiracy thinking by item.

```{r exp2-conspiracy-items, fig.cap="(ref:exp2-conspiracy-items)"}
BCTI_data <- exp2_long %>% 
  # bring to long format
  pivot_longer(cols = BCTI_apollo:BCTI_evolution, 
               names_to = "BCTI_item", values_to = "score") %>% 
  select(id, c(starts_with("BCTI"), score)) %>% 
  group_by(BCTI_item) %>% 
  summarize(avg_score = mean(score, na.rm=TRUE)) %>% 
  ungroup()

ggplot(BCTI_data, aes(x = reorder(BCTI_item, avg_score), y = avg_score)) +
    geom_pointrange(aes(ymin = 1, ymax = avg_score),
                  # Make the lines a little thicker and the dots a little bigger
                  fatten = 2, size = 1) +
  scale_y_continuous(limits = c(1, 9), breaks = seq(1, 9, 1)) +
  labs(x = "Conspiracy item", y = "Average score") +
  coord_cartesian(ylim = c(1, 9)) +
  coord_flip()
```

### By category

[To do]

### All raw answers

kbl(table, booktabs = T, longtable = TRUE,
    caption = "Reasons for consensus rejection") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2) %>%
  column_spec(3, width = "30em")

## Additional plots

(ref:exp2-conditional-acceptance) Acceptance rates of scientific consensus, based on whether the initial response to the knowledge question was false or true.

```{r exp2-conditional-acceptance, fig.cap="(ref:exp2-conditional-acceptance)"}
plot_data <- exp2_long %>% 
  group_by(knowledge, acceptance) %>% 
  count() %>% 
  group_by(knowledge) %>% 
  mutate (share = n/sum(n)) %>% 
  mutate_if(is.numeric, round, digits = 3)

absolute_numbers <- plot_data %>% 
  group_by(knowledge) %>% 
  summarise(n = sum(n))

ggplot(plot_data, aes(x = knowledge, y = share, fill = acceptance)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, 0.1)) +
  geom_text(aes(label = paste0(round(share * 100, 1), "%")),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3) +
  scale_fill_viridis_d(option = "cividis") +
  labs(x = "Knowledge answer", fill = "Acceptance \nof consensus") +
  plot_theme  +
  geom_bracket(data = absolute_numbers,
               aes(xmin = as.numeric(factor(knowledge)) - 0.4, 
                   xmax = as.numeric(factor(knowledge)) + 0.4, 
                   y.position = 1.05, label =  paste0("n = ", n)),
               inherit.aes = FALSE,
               step.increase = 0)
```

(ref:exp2-plot-overview) **A** Shows the distribution of science knowledge (left) and acceptance of scientific consensus for participants who gave the wrong answer **B** Shows the relationship between trust in science and science knowledge/acceptance (if wrong at first, rounded to the first digit) of scientific consensus **C** Shows the relationship between conspiracy thinking and science knowledge/acceptance (if wrong at first) of scientific consensus
```{r exp2-plot-overview, fig.cap="(ref:exp2-plot-overview)", fig.height= 12, fig.width=12}

@@

>>>>

In experiment 1, we tested whether participants would accept the scientific consensus on basic science facts. In most instances they did, but not always. In experiment 2, we wanted to test whether this reluctance was because of participants not trusting us as a source of consensual science knowledge. To do so, we added an explanation and sources to each consensus statement, instead of only stating the consensus. To better understand reasons for consensus rejection, after having answered all questions, we asked participants an open-ended question to explain why they rejected the consensus, for each question on which they did so. We also excluded the where do trees their materials from, as this question clearly seemed to be an outlier where most participants would get the answer wrong.

@@

Confirming results from experiment 1, we find that the more people are knowledgeable about science and the more they tend to accept the scientific consensus even when they are not that knowledgeable in science, the more they tend to trust science. These correlations are relatively weak, which might be partly due to ceiling effects: (i) most people do trust science, and (ii) that is true even among people with low knowledge or acceptance rates. Below, we show that these results hold for our alternative measures of trust and conspiracy thinking. We also include more descriptive statistics, such as knowledge and acceptance by science questions.

Regarding RQ1, participants answered on average `r exp2_descriptives$means$knowledge_mean` (sd = `r exp2_descriptives$means$knowledge_sd`) of the questions correctly, and accepted the scientific consensus on average for `r exp2_descriptives$means$acceptance_mean` (sd = `r exp2_descriptives$means$acceptance_sd`) of the questions. In response to RQ2, in most cases (`r exp2_descriptives$conditional_acceptance$false$Yes$share`), participants readily accepted the scientific consensus after having initially given the wrong answer to a question. In very few cases (`r exp2_descriptives$conditional_acceptance$true$No$share`), participants who gave the correct response afterwards rejected the scientific consensus, thereby contradicting their own initial response.

@@

For RQ3, we got `r exp2_descriptives$justifications_n` answers from `r exp2_descriptives$justifications_n_participants` different participants to the open-ended questions on why they had rejected the scientific consensus on a particular question. Table \@ref(tab:exp2-justifications) summarizes these answers by five categories. All answers can be read in below.

@@

(ref:exp2-plot-overview) Summary plot for Study 2. **A** Shows the distribution of science knowledge (left) and acceptance of scientific consensus for participants who gave the wrong answer **B** Shows the relationship between trust in science and science knowledge/acceptance (if wrong at first, rounded to the first digit) of scientific consensus **C** Shows the relationship between conspiracy thinking and science knowledge/acceptance (if wrong at first) of scientific consensus

```{r exp2-plot-overview, fig.cap="(ref:exp2-plot-overview)", fig.height= 12, fig.width=12}

@@

kbl(table, booktabs = T, longtable = TRUE,
    caption = "Reasons for consensus rejection (raw answers)") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2) %>%
  column_spec(3, width = "30em")
